О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
belongs -> is situated when needed

\begin{problem}
	\label{prb:square_side_length_and_diameter_power}
	Is there a number $\delta < 1$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	belongs to a square of side length $d^\delta$?
\end{problem}
If the answer for Problem~\ref{prb:square_side_length_and_diameter_power} is affirmative,
then we can build an estimate better than linear.

\begin{problem}
	\label{prb:square_side_length_and_diameter_linear}
	What are the maximal numbers $\delta \leq 1$ and $h \leq 0$
	such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	belongs to a square of side length $\delta d - h$?
\end{problem}

@@

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	belongs to $\mathcal{S}$?
\end{problem}
This problem in another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is a right triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the probable counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).

@@

	\item
		to belong vs. to be situated

>>>>

\begin{problem}
	\label{prb:square_side_length_and_diameter_power}
	Is there a number $\delta < 1$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $d^\delta$?
\end{problem}
If the answer for Problem~\ref{prb:square_side_length_and_diameter_power} is affirmative,
then we can build an estimate better than linear.

\begin{problem}
	\label{prb:square_side_length_and_diameter_linear}
	What are the maximal numbers $\delta \leq 1$ and $h \leq 0$
	such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $\delta d - h$?
\end{problem}

@@

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in  $\mathcal{S}$?
\end{problem}
This problem in another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is a right triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the probable counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).

@@
